---
title: "R Coding Basics"
name: "Rezoan Hossain"
output:
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
```


1.  Why does this code not work?

```{r}
#| error: true

my_variable <- 10
my_varıable
```

Look carefully! (This may seem like an exercise in pointlessness, but training your brain to notice even the tiniest difference will pay off when programming.)

**why it fails:**
1) You created the object named `my_variable`.
2) On the next line you typed `my_varıable` — that looks the same, but it uses a different character: `ı` (dotless i), not the normal `i`.
3) R is picky (in a good way): different characters = different object name, so it says “object not found”.

**Fix:** type the exact same name you created: `my_variable`.



2.  Tweak each of the following R commands so that they run correctly:


```{r}

# Step 1: load the package correctly
library(tidyverse)

# Step 2: fix the ggplot code (spelling + commas + quotes + parentheses)
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(method = "lm")
```


3.  Press Option + Shift + K / Alt + Shift + K. What happens? How can you get to the same place using the menus?

**What happens (step-by-step):**

1) RStudio opens the **Keyboard Shortcuts Help** window.
2) You can scroll/search to see shortcuts.

**Same place using menus:** `Tools` → `Keyboard Shortcuts Help`.



4.  Run the following lines of code. Which of the two plots is saved as `mpg-plot.png`?  Why?

```{r}
#| eval: false

my_bar_plot <- ggplot(mpg, aes(x = class)) +
  geom_bar()
my_scatter_plot <- ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()
ggsave(filename = "mpg-plot.png", plot = my_bar_plot)
```


**Answer**

1) `ggsave()` saves **`my_bar_plot`**.

2) Why? Because you told it exactly which plot to save: `plot = my_bar_plot`.

3) If you remove `plot = ...`, then `ggsave()` saves the **last plot you printed**.
